\documentclass[11pt]{article}

\usepackage[a4paper,margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage{hyperref}
\usepackage{microtype}

\title{Streaming Signal Platform (SSP): Event-Time Replayable Early Warning with Calibrated Alerts and RCA}
\author{SSP Authors}
\date{\today}

\begin{document}
\maketitle

\begin{abstract}
SSP is a streaming and replay platform for early-warning anomaly alerts with calibrated false-alarm control and root-cause localization. The system integrates event-time semantics, deterministic replay, first-class contract checks, and unified evaluation metrics. SSP includes filtering/fusion, prognostics, and forecasting heads that share the same infrastructure.
\end{abstract}

\section{Introduction}
Operational telemetry streams must handle late and out-of-order data while still emitting reliable alerts. False alarms under drift, missing root cause, and non-replayable evaluation are common failure modes. SSP addresses these with event-time correct streaming, deterministic replay, calibrated alerting, and RCA validated by synthetic ground truth.

\section{System overview}
SSP is composed of:
\begin{itemize}
  \item platform core: event-time primitives, windowing, replay, sources/sinks
  \item contracts: bounds, redundancy, and spectral checks that emit structured events
  \item pipelines: P4 filtering, P1 detection, P2 prognostics, P3 forecasting
  \item workflows: orchestration, metadata, artifacts, reports
\end{itemize}

\section{Methodology}
The methodology is detailed in the docs:
\begin{itemize}
  \item event time and replay
  \item early detection metrics
  \item calibration and false alarm control
  \item RCA and drift
\end{itemize}

\section{Experiments}
Experiments are configured via YAML files under \texttt{experiments/} and run via the CLI. Synthetic generators provide ground truth for correctness validation without requiring large real datasets.

\section{Conclusion}
SSP provides a coherent engineering platform for reliable early-warning detection on streaming signals, with determinism, calibration, and attribution built in.
\end{document}
